Evaluating the Supportive Effect of Feature Selection Methods on Machine Learning Models in Monitoring Forest Health Using Hyperspectral Remote Sensing Data

### 2020-04-05 docs/00-manuscripts/ieee/ieee-manuscript.tex
AB-review: style
AB-review: address PCA content remarks

% Wrapper approach
\noindent Wrappers \cite{chandrashekar2014, kohavi1997} apply search algorithms such as 'random search' or 'generic simulated annealing'.
First a (random) subset of features is chosen based on the selected algorithm.
In comparison to filters, no ranking is done in this step.
Now the model is fitted on the data and the performance is evaluated.
This is done multiple times, depending on the defined stopping criteria set by the user (performance, runtime, evaluations).
A disadvantage of this approach is that hyperparameter tuning can only be applied after the feature selection optimization finished.
Hence, the 'wrapper approach' is an expensive optimization method because two stages need to be run in sequential order.
Due to their extensive runtimes, wrappers were not considered in this work.

% PCA
A method with a completely different approach compared to filters and wrappers is the \ac{PCA}\cite{pearson1901, jolliffe2016}.
Here, the main components of the feature space are extracted and combined.
Most often the first two extracted main components are used since these contain the major information of the covariates.
By using the (automatically estimated) explained variance of the main components, the model can rely on a few features containing the majority of information available in the data.
This enables cheap model fitting with balanced loss of predictor information.
The disadvantage of this methodology is the lack of interpretability because the main components cannot be related back to the original covariates.

>>>>

% Wrapper approach
\noindent Wrappers \cite{chandrashekar2014, kohavi1997} apply search algorithms such as 'random search' or 'generic simulated annealing'.
First a (random) subset of features is chosen based on the selected algorithm.
In comparison to filters, no ranking is done in this step.
Now the model is fitted on the data and the performance is evaluated.
This is done multiple times, depending on the defined stopping criteria set by the user (performance, runtime, evaluations).
A disadvantage of this approach is that hyperparameter tuning can only be applied after the feature selection optimization finished.
Hence, the 'wrapper approach' is an expensive optimization method because two stages need to be run in sequential order.
Due to their high computational cost, wrappers were not considered in this work.

% PCA
A method with a completely different approach compared to filters and wrappers is the \ac{PCA}\cite{pearson1901, jolliffe2016}.
Here, the main components of the feature space are extracted and combined.
The number of principal components needed to explain a large portion of the variance is dynamic and depends on the dataset.
In practice, this number often ranges between two and five.
By using the (automatically estimated) explained variance of the main components, the model can rely on a few features containing the majority of information available in the data.
This enables cheap model fitting with balanced loss of predictor information.
A disadvantage is the reduced interpretability due to the main components being a squashed version of the original covariates.
